Technical Report

### 2018-04-06 fully-abstract-comp/technical-report.tex
Fix a TODO, probably a transcription error caused by my illegible handwriting :).
Fix more transcription errors in the TODOs.

\section{Full Abstraction}
\lau{TODOs from last day in Leuven}
\lau{RESOLVED: components have optional main (pc/data pair)}
\lau{RESOLVED?: linking component and context requires only one main (i.e., it is undefined if both or none of the two expose main.)}
\lau{TODO: Component logical relation.}
\lau{TODO: Version of FTLR for programs.}
\lau{TODO: Component lemma for initial executable configurations.}
\lau{TODO: Executable configuration lemma.}
\lau{TODO: ... should use initial executable configuration.}
\lau{TODO: Did we agree that memory satisfaction should require $\stkb$ to be a free stack address (or at least not in the heap part)? I think we did.}
\begin{definition}
  \label{def:points-to-instr}
  A configuration $(\ms,\reg)$ {\sourcecolor or $\Phi = (\ms,\reg,\_,\_)$} is said to point to non-$\scall{}{}{}$ instruction $i$ in $A$ iff
  \[
    \reg(\pcreg) = ((\_,\_),\_,\eaddr,\aaddr) \tand \aaddr \in A
  \]
and
\[
  \decInstr{\ms(\aaddr)} = i
\]
\end{definition}

>>>>

\section{Full Abstraction}
\lau{TODOs from last day in Leuven}
\lau{RESOLVED: components have optional main (pc/data pair)}
\lau{RESOLVED?: linking component and context requires only one main (i.e., it is undefined if both or none of the two expose main.)}
\lau{TODO: Component logical relation.}
\lau{TODO: Version of FTLR for programs.}
\lau{TODO: Compatibility lemma for initial executable configuration construct, i.e. a lemma that says ``if two programs are related, then their initial executable configurations will be related''.}
\lau{TODO: A logical relation for executable configurations.}
\lau{TODO: contextual equivalence should be defined in terms of initial executable configuration.}
\lau{TODO: Did we agree that memory satisfaction should require $\stkb$ to be a free stack address (or at least not in the heap part)? I think we did.}
\begin{definition}
  \label{def:points-to-instr}
  A configuration $(\ms,\reg)$ {\sourcecolor or $\Phi = (\ms,\reg,\_,\_)$} is said to point to non-$\scall{}{}{}$ instruction $i$ in $A$ iff
  \[
    \reg(\pcreg) = ((\_,\_),\_,\eaddr,\aaddr) \tand \aaddr \in A
  \]
and
\[
  \decInstr{\ms(\aaddr)} = i
\]
\end{definition}
